\documentclass[letterpaper, 9.5pt]{article} % Further reduced base font size to 9.5pt

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{ragged2e}

\urlstyle{same}
\raggedright
\frenchspacing

\usepackage{geometry} % Using geometry package for more control over margins
\geometry{
    left=0.6in,    % Reduced left margin
    right=0.6in,   % Reduced right margin
    top=0.5in,     % Reduced top margin
    bottom=0.5in,  % Reduced bottom margin
    headheight=0in,
    headsep=0in,
    footskip=0.3in
}

\setlength{\parskip}{0.1em} % Slightly reduced paragraph spacing

\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}
\fancyfoot[LE,RO]{\footnotesize \textbf{Kathryn Long Resume}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Section title formatting - Even tighter spacing
\titleformat{\section}{\Large\bfseries\color{MidnightBlue}}{\thesection}{0em}{} % Removed space after section number
\titlespacing*{\section}{0pt}{*1.0}{*0.2} % Further reduced spacing above and below sections

% Define colors
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\definecolor{lightblue}{rgb}{0.0,0.5,0.9}
\definecolor{mygrey}{rgb}{0.6,0.6,0.6}

% Competency command - Tighter spacing
\newcommand{\competency}[1]{%
    \vspace{0.2mm} % Reduced space above competency title even more
    \textbf{#1}
    \vspace{-1.5mm} % Slightly less negative space below title
    \begin{itemize}[leftmargin=*, itemsep=0pt, parsep=0pt]
        \renewcommand{\labelitemi}{\tiny\textbullet} % Smaller bullet points
}

% Experience command - Tighter spacing
\newcommand{\experience}[4]{%
    \textbf{#1} \hfill {\footnotesize #2} \\ % Slightly smaller date font
    \textit{#3} \hfill \textit{#4}
    \vspace{0.2mm} % Reduced space above experience description
    \begin{itemize}[leftmargin=*, itemsep=0pt, parsep=0pt]
        \renewcommand{\labelitemi}{\tiny\textbullet} % Smaller bullet points
}

% Education command - Tighter spacing
\newcommand{\education}[3]{%
    \textbf{#1} \\
    \textit{#2, #3}
    \vspace{0.2mm} % Reduced space after education entry
}

\begin{document}

% Contact Information Header - Even smaller font size
\begin{center}
    {\fontsize{17pt}{20pt}\color{darkblue}\textbf{KATHRYN LONG, ADN/ASN, RN}}\\[0.5mm] % Reduced space below name
    \fontsize{9pt}{11pt}\textbf{NICU Nurse} \href{mailto:katielong2316@gmail.com}{\underline{katielong2316@gmail.com}} $|$ 770-789-1013 $|$ Alpharetta, GA
\end{center}

\vspace{2mm} % Further reduced space after header

% Profile Section
\section{PROFILE}
\justify
Dedicated NICU Nurse with 2+ years high-acuity neonatal experience, providing holistic, family-centered care through expertise \& psychology background. Manage complex conditions, respond to emergencies, improve quality. Seeking part-time/PRN NICU RN role. % Even more condensed profile

\vspace{1mm}

% Core Competencies Section - Reorganized for compactness
\section{CORE COMPETENCIES}
\begin{itemize}[leftmargin=*, itemsep=0pt, parsep=0pt] % Top-level itemize for competencies
    \item \textbf{Advanced Neonatal Clinical Skills:} Ventilator & Oxygen Therapy, IV Access & Med Admin, Stabilization of Critically Ill Neonates, Emergency Response
    \item \textbf{Neurodevelopmental & Family-Centered Care:} Developmentally Supportive Interventions, Trauma-Informed Parent Education, Breastfeeding & Lactation Support, Family Teaching & Discharge Prep
    \item \textbf{Quality & Evidence-Based Practice:} Quality Improvement Participation, Evidence-Based Practice Implementation, Committee Leadership
    \item \textbf{Technical \& Documentation Expertise:} EMR (Epic) Proficiency, Medication & Monitoring Systems, Charting & Documentation Tools
\end{itemize}

\vspace{1mm}

% Professional Experience Section
\section{PROFESSIONAL EXPERIENCE}
\experience{NICU Nurse (Part-Time)}{June 2023 – Present}{Kennestone Hospital, Marietta, GA}{}
    \item High-quality care for complex neonates in high-acuity NICU.
    \item Rapid-response for NICU emergencies.
    \item Family education on infant care/discharge.
    \item \textbf{Committees:} \textbf{Small Baby Committee} (micro-preemie care refinement), \textbf{Infant-Driven Feeding (IDF) Core Team} (Dr. Brown's IDF program implementation). % Even more condensed experience
    \end{itemize}

\experience{OR Circulator Nurse (PRN)}{Feb – May 2023}{GA Eye Partners, Sandy Springs, GA}{} % Abbreviated month names
    \item Sterile OR environment for ophthalmic procedures.
    \item Coordinated pre-/post-op workflows.
    \end{itemize}

\experience{NICU Nurse (Full-Time Nights)}{Feb – Dec 2022}{Grady Memorial Hospital, Atlanta, GA}{} % Abbreviated month names
    \item Critical neonate care in Level III NICU.
    \item Code response, infant stabilization, RT collaboration.
    \item New nurse mentoring.
    \item Family trauma support.
    \end{itemize}

\experience{Patient Care Tech, Mother-Baby Unit}{Sep 2021 – Jan 2022}{Grady Memorial Hospital, Atlanta, GA}{} % Abbreviated month names
    \item Mother-baby couplet care support: vitals, screenings, education.
    \item Breastfeeding/bonding support.
    \item Early complication detection.
    \end{itemize}

\vspace{1mm}

% Education & Credentials Section
\section{EDUCATION \& CREDENTIALS}
\subsection*{\textbf{Education}}
\education{Associate of Science in Nursing (ASN)}{Gwinnett Technical College}{May 2021}
\education{Bachelor of Arts in Psychology (BA)}{Kennesaw State University}{May 2017}
\education{Additional Coursework}{Northeastern University}{2007–2010}


\subsection*{\textbf{Licenses \& Certifications}}
\begin{itemize}[leftmargin=*, itemsep=0pt, parsep=0pt]
    \item RN - Georgia COMPACT License
    \item Basic Life Support (BLS)
    \item Neonatal Resuscitation Program (NRP)
    \item Cardiopulmonary Resuscitation (CPR)
\end{itemize}

\vspace{1mm}

% Specialty Areas Section
\section{SPECIALTY AREAS}
\begin{itemize}[leftmargin=*, itemsep=0pt, parsep=0pt]
    \item Neonatal Critical Care: 2+ Years
    \item Operating Room/Surgical Nursing: 1 Year
    \item Mother-Baby Care: 1 Year
\end{itemize}

\end{document}